TGI Spinal Analysis Code Experiment 2

### 2023-04-14 analysis/tgi-spinal_analysis-exp1.Rmd
small changes based on pp number- checking responder rate

---
title: "TGI Spinal Analysis Code"
author: "A.G. Mitchell"
date: "2022-12-02"
output: html_document
---

@@

```{r paths}
# paths
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Raw/'
anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/Analysis/'
```

>>>>

---
title: "TGI Spinal Analysis Code Experiment 1"
author: "A.G. Mitchell"
date: "2022-12-02"
output: html_document
---

@@

```{r paths}
# paths
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Raw/'
anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Analysis/'
```

### 2023-04-14 analysis/tgi-spinal_analysis-exp2.Rmd
small changes based on pp number- checking responder rate

---
title: "TGI Spinal Analysis Code Experiment 1"
author: "A.G. Mitchell"
date: "2022-12-02"
output: html_document
---

@@

```{r paths}
# paths
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Raw/'
anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp1/Analysis/'
```

@@

# remove participant 019, stopped testing halfway due to broken thermal probe
df_res <- df_res[df_res$ID != '019' ,]
```

@@

# identify test results where pvalue is < .05
tgi$ID <- as.factor(tgi$ID)
i = 0
test = data.frame(matrix(nrow = 40, ncol = 3))
colnames(test) <- c('ID','pval','responder')

>>>>

---
title: "TGI Spinal Analysis Code Experiment 2"
author: "A.G. Mitchell"
date: "2023-04-14"
output: html_document
---

@@

```{r paths}
# paths
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp2/Raw/'
anaPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/exp2/Analysis/'
```

@@

# remove participants 047 and 048
# one had ongoing pain, the other missed 6 trials
df_res <- df_res[df_res$ID != '047' ,]
df_res <- df_res[df_res$ID != '048' ,]
```

@@

# identify test results where pvalue is < .05
tgi$ID <- as.factor(tgi$ID)
i = 0
test = data.frame(matrix(nrow = 27, ncol = 3))
colnames(test) <- c('ID','pval','responder')
